### 2019-01-23 introduction.tex
fixes of inter-arrival times and LTI

The AROT metric is essential for the project because a following aircraft is not allowed to land on the same runway before it has been vacated by the leading aircraft. The interval to the next landing aircraft is specified as the landing time interval (LTI) which is directly linked to the inter-arrival distance or in other words the wake turbulence separation. The LTI is a metric used to quantify the time separation between aircraft in a pair, derived from the distance separation between the aircraft and the final approach speed of the following aircraft.% (time travelled is distance travelled divided by velocity).

>>>>

The AROT metric is essential for the project because a following aircraft is not allowed to land on the same runway before it has been vacated by the leading aircraft. The interval to the next landing aircraft is specified as the landing time interval (LTI) which is directly linked to the inter-arrival distance or in other words the wake turbulence separation. The LTI is a metric used to quantify the time separation between aircraft in a pair, derived from the distance separation between the aircraft and the final approach speed of the following aircraft. One way the conflict between the AROT and LTI can manifest itself is through a missed approach (ICAO: bulked landing), when an aircraft landing cannot be completed due to runway incursion \cite{doc44444}: the incorrect presence of another aircraft on the runway designated for landing.% (time travelled is distance travelled divided by velocity).
